%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Karshil}{Sheth}{ %\urlstyle{same}\href{http://debarghyadas.com}{debarghyadas.com}| %\href{http://fb.co/dd}{fb.co/dd}\\
\href{mailto:karshilsheth@gmail.com}{karshilsheth@gmail.com} | (+91)9428431023 
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Indus University}
\descript{B.Tech in Computer Science \& Engineering}
\location{June 2020 | Gandhinagar, India}
\location{ Cum. GPA: 9.66 / 10.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/karshil2309}{\bf karshil2309} \\
LinkedIn://  \href{https://www.linkedin.com/in/karshilsheth}{\bf KarshilSheth} \\
StackOverflow://  \href{https://stackoverflow.com/users/7986351/karshil-sheth}{\bf karshil-sheth} \\
Hackerrank://  \href{https://www.hackerrank.com/karshil_2309}{\bf karshil-2309} \\
Quora://  \href{https://www.quora.com/Karshil-Sheth}{\bf Karshil-Sheth}\\
Hackerearth://  \href{https://www.hackerearth.com/@karshil_2309}{\bf karshil-2309}\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Data Structures \& Algorithms\\
Operating Systems \\
Computer Networks \\
Big Data Analytics \\
Object Oriented Design Principles \\
Software Lifecycle\\
Unix Tools and Scripting \\
System Design \\
Data Analytics \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
%\location{Over 5000 lines:}
Java \textbullet{}   Shell \textbullet{} Python \textbullet{} Javascript \\
PHP \textbullet{} Html5 \textbullet{} CSS3 \textbullet{} \LaTeX\ \\ 
%\location{Over 1000 lines:}
C \textbullet{} C++ \textbullet{} SQL \textbullet{} PL/SQL \\
\location{Familiar:}
Apache Solr \textbullet{} Spring-Boot \textbullet{} Android \textbullet{} Apache Camel \textbullet{} Docker \textbullet{} MySql \textbullet{} Influx DB \textbullet{} Adobe Photoshop \textbullet{} Apache Hive \textbullet{} Apache Kafka \textbullet{} AWS Services (S3, Ec2, SNS, SQS ) \textbullet{} Graphana \textbullet{} Natural Language Processing
\textbullet{} Web Development 
\sectionsep 

\section{Projects}
\subsection{}
 \href{https://github.com/karshil2309/Pizza_delivery_WebApp}{\bf Pizza Delivery Web App}\\
\href{https://github.com/karshil2309/BlockhainTask_Quillhash}{\bf Tic Tac Toe Solidity}\\ 
\href{https://github.com/karshil2309/ArCoreAdornAr Core Adorn }{\bf Ar App }
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Gateway Group of Companies}
\descript{| Software Engineer }
\location{January 2020 - Present | Ahmedabad, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Responsible to design and implement RESTFUL and XML-based web-services.
\item Work on review code as well as implementing coding standards. 
\item Worked with Services team to create and deliever Product Poc.
\item Understanding bugs and resolving same.
\item Data extraction, crawling, scrapping, data mining, file system extraction (xml, pdf, docs).
\item Giving Solutions for Search Engine of  online digtal library, with 30 millions revenue per year. 
\item During project development, I provided proof of concepts, level of efforts and coordinate with project manager and product department.
\item Administration of Kanban Board | Api Dashboard | Reports
\item Feature Development Related to Api Portal System like Skip-Check Reason, Prototype Configurations, and Encoding Strings in existing servers. 
\item Testing : Unit Testing, Integration Testing, Smoke Test for Api’s
\item Api Creation, Api Subscription, Deployment to different environments
\item Understanding system architecture and business needs with Solution Architects, Integration Architect, and Business Managers.
\item Solving Bug issues for clients and stake holders as per business requirements.
\end{tightemize}
\sectionsep

\runsubsection{Kody Technolab Pvt Ltd}
\descript{| Software Engineering Intern }
\location{June 2019 – July 2019 | Ahmedabad, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Prepared System Specification Document for the Project.
\item Responsible for creating a video chat application.
\item \href{https://github.com/karshil2309/Webrtc_Android_login}{\bf Project Code Github}
\end{tightemize}
\sectionsep

\runsubsection{Optimus Dm}
\descript{| Software Engineering Intern }
\location{December 2018 – January 2019 | Ahmedabad, India}
\begin{tightemize}
\item Responsible to develop user interface for the Digital Marketing Workshop.
\item Activities like user payment, registration, slot booking were monitored from Admin's Panel.
\item Developed Single Page Application for a Fashion Model.
\item \href{https://karshil2309.github.io/Website_Workshop/}{\bf Project Link}

\end{tightemize}
\sectionsep

\runsubsection{Rapidops Solutions Pvt ltd}
\descript{| Web Developer Intern}
\location{June 2018 – July 2018 |Ahmedabad, India}
\begin{tightemize}
\item Created Web Design Layout Templates using Abode Photoshop.
\item Worked closely with Senior Developer to document the end to end process.
\item Developed a static web page using Html5, CSS3.
\end{tightemize}
\sectionsep

\runsubsection{SilverWing Technologies Pvt Ltd}
\descript{| Web Designer Intern}
\location{August 2017 |Ahmedabad, India}
\begin{tightemize}
\item Creating Different games and Blogging website.
\item Technologies: Html5, Css3, Bootstrap
\item \href{https://github.com/karshil2309/Practice_FrontEnd}{\bf Github Link}
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Research}
% \runsubsection{Cornell Robot Learning Lab}
% \descript{| Researcher}
% \location{Jan 2014 – Jan 2015 | Ithaca, NY}
% Worked with \textbf{\href{http://www.cs.cornell.edu/~ashesh/}{Ashesh Jain}} and \textbf{\href{http://www.cs.cornell.edu/~asaxena/}{Prof Ashutosh Saxena}} to create \textbf{PlanIt}, a tool which  learns from large scale user preference feedback to plan robot trajectories in human environments.  
% \sectionsep

% \runsubsection{Cornell Phonetics Lab}
% \descript{| Head Undergraduate Researcher}
% \location{Mar 2012 – May 2013 | Ithaca, NY}
% Led the development of \textbf{QuickTongue}, the first ever breakthrough tongue-controlled game with \textbf{\href{http://conf.ling.cornell.edu/~tilsen/}{Prof Sam Tilsen}} to aid in Linguistics research. 
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2020	  &State    & Participated in SSIP Hackathon organized By Gujarat Government\\
2019	  &2\textsuperscript{nd}/50   & SPARX of Instincts’19 ( Coding Competition ) \\
2017	     & International  & \href{https://www.credly.com/badges/f9998842-1285-4c07-a515-8f45c765866c/linked_in_profile}{\bf Oracle Certified Java Programmer}\\
2017     & A+ Grade  & C Certified C-DAC GIST PACE by Government of India  \\
2012     & A Grade  & Elementary Intermediate Drawing Examination\\
2010     & 2\textsuperscript{nd} & International Mathematics Olympiad (IMO) \\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
