%------------------------
% Resume Template
% Author : Karshil Sheth
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Karshil Sheth}} & Email: \href{mailto:}{karshilsheth@gmail.com}\\
 Mobile:~~~+919428431023 \\
  \href{https://linktr.ee/karshilsheth}{Visit Profile: \textbf{LinkTree}} \\
\end{tabular*}

%----------Experience-----------------
\vspace{-5pt}
\vspace{2mm}
\section{Experience}
 \resumeSubheading{Openbet India Pvt Ltd (Endeavor)}{Oct-2022 - Present}
    {}{Software Engineer L2 (Full-time)}
    \begin{itemize}
    \setlength\itemsep{0em}
            \item Document and draw diagrams for full application flows and data flows. 
            \item Leveraged Java and Spring to optimize the betting platform, resulting in a 30\% reduction in response time, leading to increased user satisfaction and more bets placed.
 \item Worked on a real-time odds calculation engine using Java and Spring, reducing latency by 40\%, which enabled the platform to provide the latest odds to users instantly, driving higher engagement.
  \item Ensured platform compliance with legal requirements in the betting industry by implementing security measures and reporting mechanisms using Java and Spring, minimizing legal risks and avoiding fines.
\item Established comprehensive monitoring and alerting systems with Spring Actuator, reducing system downtime by 20\% through proactive issue detection and resolution.
\item Conducted A/B tests on user interface improvements, using Java to build the necessary backend services, leading to a 5\% increase in user engagement and conversion rates.
\item Prioritised customer requirements, ensuring a customer-centric approach to solution development.
\item Proactively addressed security vulnerabilities and emphasised code quality and maintainability.

            \item Analyzing the requirement and doing technical discussion for the possible approaches.
             \item Maintaining the different versions of applications to maximize the product revenue by 20\% 
              \item Responsible to design and implement ProtoBuff and Restful web-services in Spring Boot.
        \item Responsible for code reviewing as well as implementing coding standards.
            \end{itemize}
\vspace{-5pt}
  \vspace{2mm}
   \resumeSubheading{Surekha Technologies Pvt Ltd}{Feb 2022 - Oct 2022}
    {}{Software Engineer (Full-time)}
    \begin{itemize}
    \setlength\itemsep{0em}
            \item Working as Full Stack developer in Banking/ Finance Domain for an Enterprise Application.
            \item Responsible for Integration of Back-end Services and Creating Functionalities for different Screens.
             \item Responsible for Centralized logging of Liferay logs using Containerized ELFK tech stack.
             \item Developed Open API structure in YAML format that performs CRUD operations on custom entity.
             \item Implemented Custom Finder methods, Custom SQL and
DynamicQuery at service layer for specific Web Services to reduce developers time by 25\%.
             \item Designed REST API's and have understanding of the end to end flow.
              \item Solved Complex Problems like password rotation policy, insertion of 1GB of data into database using Data Structures and Algorithms.
              \item Worked on Creating Web services using spring front end controller which reduces the unauthorized call on the browser.
              
            \end{itemize}
\vspace{-5pt}
\vspace{3mm}
    \resumeSubheading
		{AutoFacets LLP ( Gateway Group of Companies) }{Jan 2020 - Jan 2022}
		{}{Software Engineer (Full-time)}
	\begin{itemize} 
	\setlength\itemsep{0em}
        \item Consulted Clients, Analyzed process flow, prepared design documents, took part in project scrum meetings.
        \item Tasks done related to Data extraction, crawling, scrapping, data mining, file system extraction (xml,pdf, docs).
        \item Provided technical guidance for Backend team for Online Digital Library, with 30 {\million}{\text{million}} revenue year.
         \item Daily Task of Administration of Kanban Board, Api Dashboard's,  Reports Visualization of Testing and Handling Data Traffic.
         \item Feature Development Related to Api Portal System like Skip-Check
Reason, Prototype Configurations, and Encoding String Check in
existing servers.
     \item Done Unit Testing, Integration Testing, Smoke Test for the functionalities created.
     \item Responsible Api Creation, Api Subscription, Deployment to 1000+ different environments for different teams.
     \item Solving Bug issues for clients and stakeholders as per business
requirements like token validation, server configuration, subscription
testing, support tasks for maintenance of existing development.
     \end{itemize}
\vspace{-5pt}
\vspace{2mm}
\section{Skills Summary}
	\resumeSubHeadingListStart
	\resumeSubItem{Languages}{~~~~~~Java 8,11,17, JavaScript, Html5, CSS3, SQL, C, C++ }
	\resumeSubItem{Frameworks}{~~~~Spring Core, Spring MVC, Spring Boot, Rest Api, Soap Api, Hibernate, Apache Camel, Liferay DXP 7.X, }{~~~~~~~~~~~~~~~~~~~~~~ Android, Axios, JQuery, Ajax, ELK, JSP, Servlets, Apache Kafka, Hadoop, Hive, JPA, Open API }
	\resumeSubItem{Tools}{~~~~~~~~~~~~~~Docker, GIT, MySQL,Influx DB, Grafana, Jenkins, Solr, Ant, Maven, Gradle, Tomcat, Nginx, Splunk, Jfrog, Posgresql }
	\resumeSubItem{Platforms}{~~~~~~~Linux, Centos, Windows, AWS - EC2, SQS, SNS, Lambda}
	\resumeSubItem{Soft Skills}{~~~~~~~Leadership, Event Management, Writing, Public Speaking, Time Management}

\resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\vspace{-5pt}
\vspace{2mm}
\section{~~Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indus University}{Gandhinagar, India}
      {Bachelor of Technology - Computer Science Engineering;  GPA: 9.66}{September 2016 - June 2020}
      {\scriptsize \textit{ \footnotesize{\newline{}\textbf{Courses:} Operating Systems, Data Structures, Analysis Of Algorithms, Networking, Databases, System Design}}}
    \resumeSubHeadingListEnd

%-----------Awards-----------------
\vspace{-5pt}
\vspace{2mm}
\section{Honors and Awards}

\begin{description}[font=$\bullet$]

\item  \href{https://www.credly.com/badges/f9998842-1285-4c07-a515-8f45c765866c/linked_in_profile}{Oracle Certfied Java Professional - May, 2018}
\vspace{-5pt}
\item {Participated in SSIP Hackathon organized By Gujarat Government - 2020 }
\vspace{-5pt}
\item {Winner in Spark Instincts Coding Competition}
\vspace{-5pt}
\item { A+ Grade C Certified C-DAC GIST PACE by Government of India - 2017 }
\vspace{-5pt}
\item { Winner in International Mathematics Olympiad (IMO) }

\end{description}

\end{document}